### 2018-07-28 Authors/Bill Munro/Peter.tex
Explored dropcaps

\usepackage[pdftex]{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}
\usepackage{url}
\usepackage{makeidx}
\usepackage{nomencl}
\usepackage{colortbl}
\usepackage[section]{placeins}
\usepackage{qcircuit}
\usepackage{array}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{mdframed}
\usepackage{dcolumn}% Align table columns on decimal point

@@

In the previous section (Sec.~\ref{sec:ent_ultimate}) we concluded that quantum networks specialising purely in entanglement distribution (Bell-pairs in the simplest case), would already be extremely capable in enabling many distributed quantum protocols. This motivates the development of protocols for entanglement distribution over noisy, long-distance quantum networks.

>>>>

\usepackage[pdftex]{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}
\usepackage{url}
\usepackage{makeidx}
\usepackage{nomencl}
\usepackage{colortbl}
\usepackage[section]{placeins}
\usepackage{qcircuit}
\usepackage{array}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{mdframed}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{type1cm}
\usepackage{lettrine}

@@

\lettrine[lines=3, findent=3pt, nindent=0pt]{I}{n} the previous section (Sec.~\ref{sec:ent_ultimate}) we concluded that quantum networks specialising purely in entanglement distribution (Bell-pairs in the simplest case), would already be extremely capable in enabling many distributed quantum protocols. This motivates the development of protocols for entanglement distribution over noisy, long-distance quantum networks.

### 2018-07-28 Sections/economics_of_the_quantum_internet.tex
typos
Explored dropcaps

One parameter that appears ubiquitously in the upcoming economic models is the computational power of a quantum computer per qubit. This relates the power and size of the computer. We define this as the \textit{network price scaling factor},

@@

Let the dollar cost of physical qubits follow Moore's Law-like dynamics, decreasing exponentially with time,
\begin{postulate}[Hardware cost]\label{post:hardware_cost}\index{Hardware cost}
The dollar-cost of a single physical qubit scales inverse exponentially as,
\begin{align}
	C(t) = C_0 {\gamma_C}^{-t},
\end{align}
where \mbox{$\gamma_C\geq 1$} characterises the decay rate.
\end{postulate}

@@

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time, per FLOP is,
\begin{align}\index{Cost of computation postulate}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} P(t)}{V(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)},
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

\begin{definition}[Quantum computational leverage] \label{def:quant_econ_lev}\index{Quantum computational leverage formula}\index{Single-qubit quantum computational leverage}
For the $i$th node, and with scaling function $f_{sc}$, the QCL is defined as the ratio between the unified time-shared and individual classical-equivalent algorithmic runtimes,
\begin{align}
\lambda_i &= \frac{\tau_i}{t_i} \nonumber \\
&= \frac{n_i}{n_\mathrm{global}} \cdot \frac{f_{sc}(n_\mathrm{global})}{f_{sc}(n_i)}, \nonumber \\
&= \frac{\chi_\mathrm{sc}(n_\mathrm{global})}{\chi_\mathrm{sc}(n_i)},\nonumber\\
\lambda_i^\mathrm{dB} &= 10\log_{10}(\lambda_i),
\end{align}
where,
\begin{align}
	n_\mathrm{global} = \sum_{j\in \mathrm{nodes}} n_j,
\end{align}
is the total number of qubits in the network.
\end{definition}

@@

\begin{definition}[Political leverage]\index{Political leverage}
The political leverage is the ratio between the computational leverages of two parties residing on the same shared network,
\begin{align}
	\gamma_{A,B} &= \frac{\lambda_A}{\lambda_B}\nonumber\\
	&= \frac{\chi_\mathrm{sc}(n_B)}{\chi_\mathrm{sc}(n_A)},\nonumber\\
	\gamma_{A,B}^\mathrm{dB} &= 10\log_{10}(\gamma_{}).
\end{align}
\end{definition}
Note that when two parties are of equal size, there is no power asymmetry and \mbox{$\gamma_{A,B}=1$}. Otherwise, when $A$ and $B$ are unequal, then \mbox{$\gamma_{A,B}\neq 1$}, indicative of power asymmetry. With linear (classical) scaling functions, the political leverage is always unity, \mbox{$\gamma_{A,B}=1$}, regardless of any size asymmetry, whereas for super-linear scaling functions the political leverage diverges.

>>>>

One parameter that appears ubiquitously in the upcoming economic models and warrants a definition of its own is the computational power of a quantum computer per qubit. This relates the power and size of the computer. We define this as the \textit{network price scaling factor},

@@

Let the dollar cost of physical qubits follow Moore's Law-like dynamics, decreasing exponentially with time,
\begin{postulate}[Hardware cost]\label{post:hardware_cost}\index{Hardware cost}
The dollar-cost of a single physical qubit scales inverse exponentially against time as,
\begin{align}
	C(t) = C_0 {\gamma_C}^{-t},
\end{align}
where \mbox{$\gamma_C\geq 1$} characterises the decay rate.
\end{postulate}

@@

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation postulate}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} P(t)}{V(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)},
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

\begin{definition}[Quantum computational leverage] \label{def:quant_econ_lev}\index{Quantum computational leverage formula}\index{Single-qubit quantum computational leverage}
For the $i$th node, and with scaling function $f_{sc}$, the QCL is defined as the ratio between the unified time-shared and individual classical-equivalent algorithmic runtimes,
\begin{align}
\lambda_i &= \frac{\tau_i}{t_i} \nonumber \\
&= \frac{n_i}{n_\mathrm{global}} \cdot \frac{f_{sc}(n_\mathrm{global})}{f_{sc}(n_i)}, \nonumber \\
&= \frac{\chi_\mathrm{sc}(n_\mathrm{global})}{\chi_\mathrm{sc}(n_i)},\nonumber\\
\lambda_i^\mathrm{dB} &= 10\log_{10}(\lambda_i),
\end{align}
where,
\begin{align}
	n_\mathrm{global} = \sum_{j\in \mathrm{nodes}} n_j,
\end{align}
is the total number of qubits in the network. The logarithmic version of the representation in decibels is simply a convenience when dealing with exponential scaling functions.
\end{definition}

@@

\begin{definition}[Political leverage]\index{Political leverage}
The political leverage is the ratio between the computational leverages of two parties residing on the same shared network,
\begin{align}
	\gamma_{A,B} &= \frac{\lambda_A}{\lambda_B}\nonumber\\
	&= \frac{\chi_\mathrm{sc}(n_B)}{\chi_\mathrm{sc}(n_A)},\nonumber\\
	\gamma_{A,B}^\mathrm{dB} &= 10\log_{10}(\gamma_{A,B}).
\end{align}
\end{definition}
Note that when two parties are of equal size, there is no power asymmetry and \mbox{$\gamma_{A,B}=1$}. Otherwise, when $A$ and $B$ are unequal, then \mbox{$\gamma_{A,B}\neq 1$}, indicative of power asymmetry. With linear (classical) scaling functions, the political leverage is always unity, \mbox{$\gamma_{A,B}=1$}, regardless of any size asymmetry, whereas for super-linear scaling functions the political leverage diverges.

### 2018-07-28 Sections/quantum_repeater_networks.tex
Explored dropcaps

Any useful future quantum internet is going to require the communication of quantum information over arbitrarily long distances. While intercity communication might be implemented via point-to-point connections\index{Point-to-point}, intracity and intercontinental communication will require extremely long distance links, well beyond the attenuation length of the optical fibres connecting them.

@@

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the Earth's curvature\index{Earth curvature}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell-pairs\index{EPR pairs}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variable states}.

@@

The links are now over much shorter distances and so can be generated with far higher probability \cite{}. Then by stitching these together using entanglement swapping (Sec.~\ref{sec:swapping})\index{Entanglement swapping}, we can generate our required long-range entanglement link \cite{}.

Beginning from this simple principle, the field of quantum repeater networks has grown enormously, leading to several generations of repeater designs, of ever increasing power and sophistication, and ever increasing technological demands.

@@

In a quantum repeater network, there are three main operations required \cite{}:
\begin{enumerate}
\item Entanglement distribution (Sec.~\ref{sec:reps_ent_dist}): to create entangled links between adjacent repeater nodes \cite{}.
\item Entanglement purification (Sec.~\ref{sec:reps_ent_purif}): to improve the quality of entanglement between nodes \cite{}\index{Entanglement purification}.
\item Entanglement swapping (Sec.~\ref{sec:reps_ent_swap}): to join adjacent entangled links together to form longer distance links \cite{}\index{Entanglement swapping}.
\end{enumerate}
The basic operation of a repeater, as shown in Fig.~\ref{fig:repeaters_2}, works as follows:

We begin our preparation of a long-range entangled link by creating multiple entangled pairs between adjacent repeater nodes (the number will depend both on the quality of the pairs we initially generate and also the target quality we want our final pair to have). Once we have enough pairs established between two repeater nodes, we perform entanglement purification\index{Entanglement purification}, which converts multiple entangled links (pairs) into a fewer number with higher quality. 
\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{repeaters_2}
\caption{Basic operation of a (first generation) quantum repeater network. (a) Preparation of multiple entangled links between adjacent repeater nodes. (b) They are then purified to create higher fidelity links. (c) Entanglement swapping between adjacent pairs creates links of twice the original length. (d) These new links are purified to create higher fidelity ones. (e) Entanglement swapping in creates a link four times the original size. This process continues as necessary to reach target distance and purity.} 
\label{fig:repeaters_2}
\end{figure} 
These purification steps, shown in Fig.~\ref{fig:repeaters_2}(a-b), are performed on the links between all adjacent repeaters, increasing the quality of the links between those adjacent repeater stations to the required degree. Entanglement swapping, as shown in Fig.~\ref{fig:repeaters_2}(c), then creates links twice as long. The resulting entanglement links can then be used for further rounds of purification and swapping until one generates a high quality link between the desired points in the network \cite{}.

@@

Probably the most important operation for any quantum repeater setup is entanglement distribution, the process of creating entanglement between two remote parties (Alice and Bob) connected by a quantum channel (generally an optical fibre or free-space link). This can be implemented in a number of ways \cite{bib:Bennett96, bib:enk98, bib:bennett93, bib:SSRG09, bib:childress06, bib:loock06, bib:munro08}, but can be broadly categorised into three basic schemas:
\begin{itemize}
\item Photon emission from quantum memories in the repeater nodes, followed by which-path erasure.\index{Which-path erasure}
\item Absorption of entangled photons by quantum memories.
\item Photon emission at one node and absorption at another.
\end{itemize}
By far, the emission based schemes are the most common, which we concentrate on here. Such schemes operate by using an entanglement process -- \textit{which-path erasure} -- to entangle two quantum memories via photons to which they were coupled.

@@

Ideally one wants to generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
|\Psi\rangle=\frac{1}{\sqrt{2}} (|g\rangle |H\rangle + |e\rangle |V\rangle),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of light. 
\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{repeaters_3}
\caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitter}\index{Polarising beamsplitter} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
|\Psi\rangle &= \frac{1}{2} |g\rangle |g\rangle |H\rangle |H\rangle +\frac{1}{2} |e\rangle |e\rangle |V\rangle |V\rangle \nonumber \\
&+\frac{1}{2} |g\rangle |e\rangle |HV\rangle |0\rangle + \frac{1}{2} |e\rangle |g\rangle |0\rangle |HV\rangle. 
\end{align}

One immediately notices that the $|g\rangle |e\rangle$ and $|e\rangle |g\rangle$ contributions are associated with two photons in one of the PBS exit modes, the other being in the vacuum state. However, the $|g\rangle |g\rangle$ and $|e\rangle |e\rangle$ terms have one photon in each of the output modes. They are of opposite polarisation, but measuring those photons in the diagonal/anti-diagonal ($\hat{X}$) basis erases this `which-path' information yielding an equal superposition of the two alternative histories -- an entangled state of the form,
\begin{align}
|\Psi_\pm\rangle=\frac{1}{\sqrt{2}} (|g\rangle |g\rangle \pm |e\rangle |e\rangle),
\end{align}
where the sign is given by the parity of the two photo-detection outcomes in the $\hat{X}$ basis. This entangled state is stored in the quantum memories between nodes \cite{}.

The scheme based on photon absorption by the quantum memories is effectively the time reversal of the emission-based scheme \cite{}. Instead of using the beamsplitter to entangle the photons emitted from each memory, a source of entangled photon(s) is employed \cite{}. Of course, the emission and absorption schemes can be used together in a hybrid architecture.

In any entanglement distribution scheme for quantum networks, the repeater nodes are spatially separated and one must consider channel losses, which are the dominant error source. Channel loss in this situation implies that we do not register a coincidence event between $D_1$ and $D_2$, which heralds the entanglement. Thus our entanglement distribution success probability is reduced. In fact, the heralded probability of success can be expressed as \cite{},
\begin{align}
p_\mathrm{ED}= \frac{1}{2} e^{-L/L_0} {p_\mathrm{det}}^2,
\end{align} 
where $L$ is the distance between the two repeater nodes with $L_0$ being the attenuation length of the channel, while $p_\mathrm{det}$ is the detector efficiency. Here we have ignored the source and coupling efficiencies. It is immediately obvious from this expression that the further the repeater nodes are apart, the lower the probability of success, on an exponentially decaying trajectory. The attenuation length of typical telecom optical fibre is approximately 22.5km and so the average time to generate a distributed entangled pair is,
\begin{align}
T_\mathrm{av} &\sim \frac{L}{ c \cdot p_\mathrm{ED}}\nonumber\\
&= \frac{2 L e^{L/L_0}}{ c \cdot {p_\mathrm{det}}^2}
\end{align} 
where $c$ is the speed of light in the channel. This grows exponentially against node separation and so places important constraints on the lifetime of the quantum memories. If we consider pure dephasing effects on our matter qubits, the state of our system can be represented by,
\begin{align}
\hat\rho(F) = F |\Psi^+\rangle \langle \Psi^+|+(1-F) |\Psi^-\rangle \langle \Psi^-|,
\label{eq:rho_bell_fid}
\end{align} 
where $F$ is the fidelity of our entangled state given by,
\begin{align}
F=\frac{1+e^{-t/\tau_\mathrm{D}}}{2},
\end{align} 
with $t$ being the duration over which the entangled state is held in memory, while $\tau_\mathrm{D}$ is the coherence time of the memory. If one only requires a single Bell pair and no further operation are performed, then \mbox{$t=c/L$}. However in a more general setting where multiple pairs are required, the time will be $T_\mathrm{av}$ on average, which is inversely proportional to the probability of generating the entangled state. The quality of the prepared remote entangled state may therefore not be sufficient for the tasks it is required for due to these finite memory lifetimes or operational gate errors. One needs to be able to purify these entangled resources.

@@

There are two common variants of these purification protocols: the Deutsch and Dur variants:
\begin{itemize}
\item \textit{Deutsch protocol} \cite{bib:Deutsch96}\index{Deutsch protocol}: This is an efficient purification protocol utilising Bell diagonal states that reaches a high fidelity in a few purification rounds. It is assumed that both entangled pairs have the same form. The purification protocol is the same at the one described above in Fig.~\ref{fig:repeaters_4}, but begins with Alice (Bob) applying $\pi/2$ $(-\pi/2)$ rotations about the $X$-axis on their qubits before the usual CNOT gates and measurements are performed. Two copies of the successfully purified pair can then be used in a recursive approach to purify either further. This in turns means multiple copies of the originally distributed states are required. We must have enough entangled pairs available to perform the multiple rounds of purification that are required, which grows exponentially with the number of purification rounds.

\item \textit{D{\"u}r protocol} \cite{bib:dur98}\index{D{\"ur} protocol}: This uses the same core purification elements as shown in Fig.~\ref{fig:repeaters_4} but relaxes the traditional constraint that both Bell pairs must have the same fidelity. Instead we begin with two pairs of the same fidelity $F$, and perform the traditional purification. If successful we perform the next round of purification using the improved fidelity pair from the previous round and a fresh fidelity $F$ pair. In effect this new auxiliary pair is used to boost the fidelity of the original pair higher. This can continue until we reach a limiting fidelity dependent on the original $F$. This limiting fidelity may be above the desired resultant fidelity, at which point we can terminate the purification protocol. A significant difference between the Deutsch and Dur protocols is that the number of memories in the Dur situation is linear in the number of nesting levels.
\end{itemize}

@@

It can be easily seen from this formula that,
\begin{align}
	T_{n,k,L_\mathrm{tot}} \gg \frac{2 L_\mathrm{tot}}{c},
\end{align}
especially if probabilistic gates are included. Next the resources scale polynomially with,
\begin{align}
	M_{n,k} &\sim 2^{(k+1)n}\nonumber\\
	&\sim \left(\frac{L_\mathrm{tot}}{L}\right)^{k+1},
\end{align}
for the Deutsch protocol, which in turn implies it is efficient. However for long distances $L_\mathrm{tot}$, our normalised rate \mbox{$R(n,k,L_\mathrm{tot})\ll 1\mathrm{Hz}$}, especially when probabilistic CNOT gates and Bell state measurements are employed \cite{bib:jiang09, bib:munro10}.

@@

Fundamentally we know that the time to attempt to generate a single entangled Bell pair between two nodes is scaling as $L/c$ (where $L$ is the distance between those two nodes). With channel losses we need to make,
\begin{align}
m=\frac{\log_{10} (\epsilon)}{\log_{10} (1-p_\mathrm{ED})} - \log_{10} (\epsilon / p_\mathrm{ED}),
\end{align}
attempts to generate a single Bell pair with error probability $\epsilon$. We can make these attempts simultaneously and not affect the generation time. Now by using a butterfly repeater design, as illustrated in Fig.~\ref{fig:repeaters_8}, one immediately notices that the qubits with the repeater nodes are only used for duration $\sim 2 L/c$. After this time those qubits have been freed up and are available to generate new entangled links. This means in turn that the time to generate the long-range entangled pair will scale as \mbox{$T\sim O(2L/c)$} (independent of the overall distance $L_\mathrm{tot}$) \cite{bib:jiang09, bib:munro10, bib:Muralidharan2016}. The exact resources used depends heavily on the error correcting code, but we know they in principe scale as \mbox{$M \sim O(\mathrm{polylog}(L_\mathrm{tot}))$} \cite{bib:Muralidharan2016}.

>>>>

Any useful future quantum internet is going to require the communication of quantum information over arbitrarily long distances. While intercity communication might be implemented via point-to-point connections\index{Point-to-point}, intracity and intercontinental communication will require extremely long distance links, well beyond the attenuation length of the optical fibres connecting them or the line-of-sight of satellites in orbit.

@@

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the curvature of the Earth\index{Curvature of Earth}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell-pairs\index{EPR pairs}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variable states}.

@@

The links are now over much shorter distances and so can be generated with far higher probability. Then by stitching these together using entanglement swapping (Sec.~\ref{sec:swapping})\index{Entanglement swapping}, we can generate our required long-range entanglement link.

Beginning from this simple principle, the field of quantum repeater networks has grown enormously, leading to several generations of repeater designs, of ever increasing power and sophistication, and ever more challenging technological demands.

@@

In a quantum repeater network, there are three main operations required:
\begin{enumerate}
\item Entanglement distribution (Sec.~\ref{sec:reps_ent_dist}): to create entangled links between adjacent repeater nodes.
\item Entanglement purification (Sec.~\ref{sec:reps_ent_purif}): to improve the quality of entanglement between nodes\index{Entanglement purification}.
\item Entanglement swapping (Sec.~\ref{sec:reps_ent_swap}): to join adjacent entangled links together to form longer distance links\index{Entanglement swapping}.
\end{enumerate}
The basic operation of a repeater, as shown in Fig.~\ref{fig:repeaters_2}, works as follows:

We begin our preparation of a long-range entangled link by creating multiple entangled pairs between adjacent repeater nodes (the number will depend both on the quality of the pairs we initially generate and also the target quality we want our final pair to have). Once we have enough pairs established between two repeater nodes, we perform entanglement purification\index{Entanglement purification}, which converts multiple entangled links (pairs) into a fewer number with higher quality. 
\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{repeaters_2}
\caption{Basic operation of a (first generation) quantum repeater network. (a) Preparation of multiple entangled links between adjacent repeater nodes. (b) They are then purified to create higher fidelity links. (c) Entanglement swapping between adjacent pairs creates links of twice the original length. (d) These new links are purified to create higher fidelity ones. (e) Entanglement swapping in creates a link four times the original size. This process continues as necessary to reach target distance and purity.} 
\label{fig:repeaters_2}
\end{figure} 
These purification steps, shown in Fig.~\ref{fig:repeaters_2}(a-b), are performed on the links between all adjacent repeaters, increasing the quality of the links between those adjacent repeater stations to the required degree. Entanglement swapping, as shown in Fig.~\ref{fig:repeaters_2}(c), then creates links twice as long. The resulting entanglement links can then be used iteratively for further rounds of purification and swapping until one generates a high quality link between the desired points in the network.

@@

Probably the most important operation for any quantum repeater setup is entanglement distribution, the process of creating entanglement between two remote parties (Alice and Bob) connected by a quantum channel (generally an optical fibre or free-space link). This can be implemented in a number of ways \cite{bib:Bennett96, bib:enk98, bib:bennett93, bib:SSRG09, bib:childress06, bib:loock06, bib:munro08}, but can be broadly categorised into three basic schemas:
\begin{itemize}
\item Photon emission from quantum memories in the repeater nodes, followed by which-path erasure.\index{Which-path erasure}
\item Absorption of entangled photons by quantum memories.
\item Photon emission at one node and absorption at another.
\end{itemize}
By far, the emission based schemes are the most common, which we will concentrate on here. Such schemes operate by using an entangling operation -- \textit{which-path erasure} -- to entangle two quantum memories via photons to which they were coupled. Effectively the process teleports the action of an entangling gate\index{Quantum gate teleportation} (Sec.~\ref{sec:teleport_gate}) acting on the photons onto the quantum memories to which they were entangled.

@@

Ideally one wants to initially generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
|\Psi\rangle=\frac{1}{\sqrt{2}} (|g\rangle |H\rangle + |e\rangle |V\rangle),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of a single photon. 
\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{repeaters_3}
\caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitter}\index{Polarising beamsplitter} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
|\Psi\rangle &= \frac{1}{2} |g\rangle |g\rangle |H\rangle |H\rangle +\frac{1}{2} |e\rangle |e\rangle |V\rangle |V\rangle \nonumber \\
&+\frac{1}{2} |g\rangle |e\rangle |HV\rangle |0\rangle + \frac{1}{2} |e\rangle |g\rangle |0\rangle |HV\rangle. 
\end{align}

One immediately notices that the $|g\rangle |e\rangle$ and $|e\rangle |g\rangle$ contributions are associated with two photons in one of the PBS exit modes, the other being in the vacuum state. However, the $|g\rangle |g\rangle$ and $|e\rangle |e\rangle$ terms have one photon in each of the output modes. They are of opposite polarisation, but measuring those photons in the diagonal/anti-diagonal ($\hat{X}$) basis erases this `which-path' information yielding an equal superposition of the two alternative histories -- an entangled state of the form,
\begin{align}
|\Psi_\pm\rangle=\frac{1}{\sqrt{2}} (|g\rangle |g\rangle \pm |e\rangle |e\rangle),
\end{align}
where the sign is given by the parity of the two photo-detection outcomes in the $\hat{X}$ basis. This entangled state is stored in the quantum memories between nodes.

The scheme based on photon absorption by the quantum memories is effectively the time reversal of the emission-based scheme. Instead of using the beamsplitter to entangle the photons emitted from each memory, a source of entangled photon(s) is employed. Of course, the emission and absorption schemes can be used together in a hybrid architecture.

In any entanglement distribution scheme for quantum networks, the repeater nodes are spatially separated and one must consider channel losses, which are the dominant error source. Channel loss in this situation implies that we do not register a coincidence event between $D_1$ and $D_2$, which heralds the entanglement. Thus our entanglement distribution success probability is reduced. In fact, the heralded probability of success can be expressed as,
\begin{align}
p_\mathrm{ED}= \frac{1}{2} e^{-L/L_0} {p_\mathrm{det}}^2,
\end{align} 
where $L$ is the distance between the two repeater nodes with $L_0$ being the attenuation length of the channel, while $p_\mathrm{det}$ is the detector efficiency. Here we have ignored the source and coupling efficiencies. It is immediately obvious from this expression that the further the repeater nodes are apart, the lower the probability of success, on an exponentially decaying trajectory. The attenuation length of typical telecom optical fibre is approximately 22.5km and so the average time to generate a distributed entangled pair is,
\begin{align}
T_\mathrm{av} &\sim \frac{L}{ c \cdot p_\mathrm{ED}}\nonumber\\
&= \frac{2 L e^{L/L_0}}{ c \cdot {p_\mathrm{det}}^2}
\end{align} 
where $c$ is the speed of light in the channel. This grows exponentially against node separation and so places important constraints on the lifetime of the quantum memories. If we consider pure dephasing effects on our matter qubits, the state of our system can be represented by,
\begin{align}
\hat\rho(F) = F |\Psi^+\rangle \langle \Psi^+|+(1-F) |\Psi^-\rangle \langle \Psi^-|,
\label{eq:rho_bell_fid}
\end{align} 
where $F$ is the fidelity of our entangled state given by,
\begin{align}
F=\frac{1+e^{-t/\tau_\mathrm{D}}}{2},
\end{align} 
with $t$ being the duration over which the entangled state is held in memory, while $\tau_\mathrm{D}$ is the coherence time of the memory. If one only requires a single Bell pair and no further operation are performed, then \mbox{$t=c/L$}. However in a more general setting where multiple pairs are required, the time will be $T_\mathrm{av}$ on average, which is inversely proportional to the probability of generating the entangled state. The quality of the prepared remote entangled state may therefore not be sufficient for the tasks it is required for due to these finite memory lifetimes or operational gate errors. One needs to be able to purify these entangled resources.

@@

There are two common variants of these purification protocols: the Deutsch and D{\"u}r variants:
\begin{itemize}
\item \textit{Deutsch protocol} \cite{bib:Deutsch96}\index{Deutsch protocol}: This is an efficient purification protocol utilising Bell diagonal states that reaches a high fidelity in a few purification rounds. It is assumed that both entangled pairs have the same form. The purification protocol is the same at the one described above in Fig.~\ref{fig:repeaters_4}, but begins with Alice (Bob) applying $\pi/2$ $(-\pi/2)$ rotations about the $X$-axis on their qubits before the usual CNOT gates and measurements are performed. Two copies of the successfully purified pair can then be used in a recursive approach to purify either further. This in turns means multiple copies of the originally distributed states are required. We must have enough entangled pairs available to perform the multiple rounds of purification that are required, which grows exponentially with the number of purification rounds.

\item \textit{D{\"u}r protocol} \cite{bib:dur98}\index{D{\"ur} protocol}: This uses the same core purification elements as shown in Fig.~\ref{fig:repeaters_4} but relaxes the traditional constraint that both Bell pairs must have the same fidelity. Instead we begin with two pairs of the same fidelity $F$, and perform the traditional purification. If successful we perform the next round of purification using the improved fidelity pair from the previous round and a fresh fidelity $F$ pair. In effect this new auxiliary pair is used to boost the fidelity of the original pair higher. This can continue until we reach a limiting fidelity dependent on the original $F$. This limiting fidelity may be above the desired resultant fidelity, at which point we can terminate the purification protocol. A significant difference between the Deutsch and D{\"u}r protocols is that the number of memories in the D{\"u}r situation is linear in the number of nesting levels.
\end{itemize}

@@

It can be easily seen from this formula that,
\begin{align}
	T_{n,k,L_\mathrm{tot}} \gg \frac{2 L_\mathrm{tot}}{c},
\end{align}
especially if probabilistic gates are included. Next the resources scale polynomially with,
\begin{align}
	M_{n,k} &\sim 2^{(k+1)n}\nonumber\\
	&= \left(\frac{L_\mathrm{tot}}{L}\right)^{k+1},
\end{align}
for the Deutsch protocol, which in turn implies it is efficient. However for long distances $L_\mathrm{tot}$, our normalised rate \mbox{$R(n,k,L_\mathrm{tot})\ll 1\mathrm{Hz}$}, especially when probabilistic CNOT gates and Bell state measurements are employed \cite{bib:jiang09, bib:munro10}.

@@

Fundamentally we know that the time to attempt to generate a single entangled Bell pair between two nodes is scaling as $L/c$ (where $L$ is the distance between those two nodes). With channel losses we need to make,
\begin{align}
m=\frac{\log_{10} (\varepsilon)}{\log_{10} (1-p_\mathrm{ED})} - \log_{10} \left(\frac{\varepsilon}{p_\mathrm{ED}}\right),
\end{align}
attempts to generate a single Bell pair with error probability $\varepsilon$. We can make these attempts simultaneously and not affect the generation time. Now by using a butterfly repeater design, as illustrated in Fig.~\ref{fig:repeaters_8}, one immediately notices that the qubits with the repeater nodes are only used for duration $\sim 2 L/c$. After this time those qubits have been freed up and are available to generate new entangled links. This means in turn that the time to generate the long-range entangled pair will scale as \mbox{$T\sim O(2L/c)$} (independent of the overall distance $L_\mathrm{tot}$) \cite{bib:jiang09, bib:munro10, bib:Muralidharan2016}. The exact resources used depends heavily on the error correcting code, but we know they in principe scale as \mbox{$M \sim O(\mathrm{polylog}(L_\mathrm{tot}))$} \cite{bib:Muralidharan2016}.
